Coherent optical association of a single molecule

### 2020-09-23 paper.tex
More figure captions for the results plots

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure*}
  \includegraphics[height=4.5cm]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman resonance from atomic state to molecular state, showing Fourier limited linewidth.
    \todo{states, time}
    (B) Rabi oscillation on resonance
    \label{f-raman}}
\end{figure*}

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Two-body atom lifetime in 15 mW of trap depth \todo{lifetime number,
      subtraction of single body, photoassociation rate}
    (B) Molecule lifetime in 15 mW of trap depth \todo{lifetime number}
    \label{f-lifetime}}
\end{figure*}

\begin{figure*}
  \includegraphics[height=4.5cm]{fig4.pdf}
  \caption{Raman Rabi frequency vs detuning
    \label{f-det}}
\end{figure*}

>>>>

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure*}
  \includegraphics[height=4.5cm]{fig2.pdf}
  \caption{
    (A) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to define the location of the
    atoms and molecule.
    We use a bias B field of $B_0=8.8 G$ alone the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    (B) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    When driving the Raman transition, the up leg power is smoothly ramped down and
    the down leg power ramped up over $10\mu s$ while maintaining the total power of the tweezer.
    This minimizes the heating on the atoms due to power fluctuation while maximizes the time
    with maximum Raman Rabi frequency when the up and down leg powers are equal.
    (C) Raman resonance from atomic state $Na(2,2)\ Cs(3,3)$ to the first molecular bound state
    using a $0.1\mathrm{ms}$ pulse.
    The full width half maximum (FWHM) of $8.43(81) \mathrm{kHz}$ of the resonance
    is consistent with the FWHM for a coherent $0.1\mathrm{ms}$ $8.0 \mathrm{kHz}$ $\pi$ pulse.
    (D) Raman pulse time scan on resonance. A decaying Rabi oscillation can be observed
    proving the coherence of the Raman transfer process.
    \label{f-raman}}
\end{figure*}

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime of $...$ is consistent with that measured from the Raman transition data.
    \label{f-lifetime}}
\end{figure*}

\begin{figure*}
  \includegraphics[height=4.5cm]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer/Raman power and detuning.
    (A) Raman Rabi frequency scales as $P_{tweezer}^{1.29}$ and follows $1/\delta$ with an offset.
    (B) Atom loss rate scales as $P_{tweezer}^{2.58}$ suggesting a two-photon scattering loss.
    (C) Molecular loss rate scales closed to $P_{tweezer}$ and follows $1/\delta^2$
    with additional detuning independent background loss rate.
    This result controdicts the our previous measurement of excited state lifetime
    suggesting that there are additional loss mechanism that is not taken into account.
    \label{f-det}}
\end{figure*}
